### 2021-12-16 documentos/pce.tex
Typo
Otro comentario sobre "PCE maps"

\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamentecanales cuánticos. Por esto, 

@@

where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.

>>>>

\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamente canales cuánticos. Por esto, 

@@

where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce:
\janote{Derivado de mi comentario sobre el uso de ``PCE maps''
también propongo que en vez de ``show that only five operations are \pce{}''
se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
channels''} 
the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
